---
title: "NoSQL"
author: "Yadu"
date: "April 11, 2016"
output: html_document
---

First, we load the required packages.

```{r}
library(RNeo4j)
library(visNetwork)
```

Next, we establish the connection to Neo4j and clear the previously existing data.

```{r}
graph = startGraph("http://localhost:7474/db/data/", username = "neo4j", password = "cometha271")
clear(graph, input = F)
```

Now, we create all of the appropriate nodes with the apporpriate labels.

```{r}
danny = createNode(graph, "Person", name = "Danny DeVito")
rhea = createNode(graph, "Person", name = "Rhea Perlman")
swank = createNode(graph, "Person", name = "Hillary Swank")
dempsey = createNode(graph, "Person", name = "Patrick Dempsey")
pam = createNode(graph, "Person", name = "Pam Ferris")
wisdom = createNode(graph, "Person", name = "Robert Wisdom")
ferrell = createNode(graph, "Person", name = "Will Ferrell")
black = createNode(graph, "Person", name = "Jack Black")
staunton = createNode(graph, "Person", name = "Imelda Staunton")
radcliffe = createNode(graph, "Person", name = "Daniel Radcliffe")

matilda = createNode(graph, "Movie", name = "Matilda")
freedom = createNode(graph, "Movie", name = "Freedom Writers")
beethoven = createNode(graph, "Movie", name = "Beethoven's Big Break")
harry1 = createNode(graph, "Movie", name = "Harry Potter and the Prisoner of Azkaban")
harry2 = createNode(graph, "Movie", name = "Harry Potter and the Order of the Phoenix")
harry3 = createNode(graph, "Movie", name = "Harry Potter and the Deathly Hallows")
cuckoo = createNode(graph, "Movie", name = "One Flew Over the Cuckoo's Nest")
anchor = createNode(graph, "Movie", name = "Anchorman")
oldschool = createNode(graph, "Movie", name = "Old School")
gulliver = createNode(graph, "Movie", name = "Gulliver's Travels")
lorax = createNode(graph, "Movie", name = "The Lorax")
panda = createNode(graph, "Movie", name = "Kung-Fu Panda")
paddington = createNode(graph, "Movie", name = "Paddington")
mars = createNode(graph, "Movie", name = "Mars Attacks!")
```

Now, we create the appropriate relations.

```{r}
createRel(danny, "DIRECTED", matilda)
createRel(danny, "ACTED_IN", matilda)
createRel(danny, "DIRECTED", freedom)
createRel(danny, "ACTED_IN", cuckoo)
createRel(rhea, "ACTED_IN", matilda)
createRel(rhea, "ACTED_IN", beethoven)
createRel(swank, "ACTED_IN", freedom)
createRel(dempsey, "ACTED_IN", freedom)
createRel(pam, "ACTED_IN", matilda)
createRel(pam, "ACTED_IN", harry1)
createRel(wisdom, "ACTED_IN", freedom)
createRel(ferrell, "ACTED_IN", anchor)
createRel(ferrell, "ACTED_IN", oldschool)
createRel(black, "ACTED_IN", anchor)
createRel(black, "ACTED_IN", gulliver)
createRel(black, "STARRED_IN", panda)
createRel(danny, "STARRED_IN", lorax)
createRel(staunton, "ACTED_IN", freedom)
createRel(staunton, "ACTED_IN", harry2)
createRel(staunton, "ACTED_IN", harry3)
createRel(radcliffe, "ACTED_IN", harry1)
createRel(radcliffe, "ACTED_IN", harry2)
createRel(radcliffe, "ACTED_IN", harry3)
createRel(staunton, "STARRED_IN", paddington)
createRel(black, "ACTED_IN", mars)
createRel(danny, "ACTED_IN", mars)

createRel(danny, "MARRIED", rhea)
```

Now we create the following node and edge queries and cypher them. 

```{r}
node_query = "
MATCH n
RETURN n.name AS id,
n.name AS label,
LABELS(n)[0] AS group
"

edge_query = "
MATCH (n) - [r] -> (m)
RETURN n.name AS from,
m.name AS to,
TYPE(r) AS label
"

nodes = cypher(graph, node_query)
edges = cypher(graph, edge_query)
```

Finally we can visualize the entire network. 

```{r}
visNetwork(nodes,edges)
```

One advantage of storing the data in Neo4j is that we would be able to extract information in a quicker way and see relationships between the people and the different movies listed. We would also be able to visualize it in a network as shown above. 